Reanalysis Step 5: Main Effects Outcome Analysis

### 2025-08-31 reanalysis-5-outcome_analysis.qmd
fix

  # Display odds ratio from contrast
  kable(contrasts_df |> 
        mutate(
          Contrast = "Lapsed vs Not Lapsed",
          Odds_Ratio = round(odds.ratio, 3),
          SE_OR = round(SE, 4),
          CI_Lower = round(asymp.LCL, 3),
          CI_Upper = round(asymp.UCL, 3),
          p.value = format.pval(p.value, digits = 4, eps = 0.0001)
        ) |>
        select(Contrast, Odds_Ratio, SE_OR, CI_Lower, CI_Upper, p.value),
        caption = "Main effect: Odds ratio for lapse effect",
        col.names = c("Contrast", "Odds Ratio", "SE", "Lower CI", "Upper CI", "P-value"))

>>>>

  # Get confidence intervals using confint if not present
  if (!("lower.CL" %in% names(contrasts_df))) {
    contrasts_ci <- confint(contrasts_lapse)
    contrasts_df <- cbind(contrasts_df, contrasts_ci[, c("lower.CL", "upper.CL")])
  }

  # Display odds ratio from contrast
  # Note: OR < 1 means lower odds in reference group (ever_lapse_binary0)
  # We want to show it as Lapsed vs Not Lapsed, so take reciprocal
  or_value <- 1 / contrasts_df$odds.ratio[1]  # Invert to get Lapsed/Not Lapsed

  or_display <- data.frame(
    Contrast = "Lapsed vs Not Lapsed",
    Odds_Ratio = round(or_value, 3),
    SE = round(contrasts_df$SE[1], 4),
    CI_Lower = round(1/contrasts_df$upper.CL[1], 3),  # Invert and swap
    CI_Upper = round(1/contrasts_df$lower.CL[1], 3),  # Invert and swap
    p.value = format.pval(contrasts_df$p.value[1], digits = 4, eps = 0.0001)
  )

  kable(or_display,
        caption = "Main effect: Odds ratio for lapse effect",
        col.names = c("Contrast", "Odds Ratio", "SE", "Lower CI", "Upper CI", "P-value"))
